%!TEX root = ../dissertation.tex
\begin{savequote}[75mm]
What do you read, my lord?

Words, words, words.
\qauthor{Hamlet, 2:2}
\end{savequote}

\chapter{Data and Simulated Samples}
\label{ch:samples}
\newthought{The data and} Monte Carlo simulation (MC) samples used in this thesis are the same as in the fiducial analysis.  The data corresponds to \LUMI of $pp$ collision data collected in 2015+16 at the ATLAS detector at $\sqrt{s}=13$ \TeV.  Details of the Run 1 analysis referenced in Chapter \ref{ch:comb}, may be found in \cite{run1note}.  Only events recorded with all systems in ATLAS in good working order and passing certain quality requirements, according to a Good Run List (GRL), are analyzed.  

Details about MC samples may be found in \cite{modelingnote}, and signal and background modeling are discussed in the next.  The \ZH\, process is considered for both multivariate analysis (MVA) optimization and the final statistical analysis, while $WH\to\ell\nu b\bar{b}$ and $ZH\to\nu\nu b\bar{b}$ production are included in the final statistical analysis only.  Signal MC samples were generated separately for $qq$ and $gg$ initiated $VH$ processes.  $qqVH$ samples were generated with \textsc{Powheg MiNLO + Pythia8} \cite{powheg0,pythia8} with the AZNLO \cite{aznlo} tune set and NNPDF3.0 PDF \cite{nnpdf3}, with alternate samples generated using \textsc{MadGraph5\_aMC@NLO} \cite{madgraph} for the hard scatter generation and \textsc{Pythia8} for the hardronization, parton shower (PS), underlying event (UE), and multiple parton interactions (MPI).
  Nominal $ggZH$ samples were generated using \textsc{Powheg} for the matrix element (ME) and \textsc{Pythia8} for the parton shower (PS), underlying event (UE), and multiple parton interactions (MPI), again applying the AZNLO tune and NNPDF3.0 PDF set. \cite{support17}

The background processes considered in these studies are $Z+$jets, \tt, and diboson production for both MVA optimization and the final statistical analysis with single top production and $W+$jets only considered in the final statistical analysis.  $V+$jets samples are generated using \textsc{Sherpa 2.2.1} \cite{support18} for both the ME and PS.  These samples are generated in different groups, according to the identity of the $V$, the $\max\left(H_T,p_T^V\right)$ of events, with further subdivisions according to the flavor of the two leading jets in an event, $b$, $c$, or $l$, for a total of six categories.  \tt\, samples are generated using \textsc{Powheg} with the NNPDF3.0 PDF set interfaced with \textsc{Pythia8} using the NNPDF2.3 PDF's and the A14 tune \cite{support19}.  Single top samples use \textsc{Powheg} with the CT10 PDF's interfaced with \textsc{Pythia6} using the CTEQ6L1 PDF's \cite{support20,support21}.  Diboson samples are generated with \textsc{Sherpa 2.2.1} interfaced with the NNPDF3.0 NNLO PDF set normalized to NLO cross sections \cite{support22}.

