%!TEX root = ../dissertation.tex
% the acknowledgments section

%\newthought{Hi, Mom!}
\newthought{An endeavor} as ponderous as PhD is not possible without the support of many, and mine was no exception.  First and foremost, I would like to thank my advisor, John Huth.  Without John's support and wisdom in physics, primitive navigation, and so much else, the last six years would have neither been possible, and I can safely say the experience would not have been nearly so intellectually fulfilling.  It has been an honor and a pleasure to have Matt Schwartz and Gary Feldman as my other two committee members, and their ideas and guidance certainly shaped the character of the research in these pages.

Doing research as a member of the ATLAS collaboration has certainly been an educational experience, and I have been very fortunate to have Harvard ATLAS members past and present as colleagues.  Many thanks to Professors Melissa Franklin and Masahiro Morii for their sage counsel and genuine care for students on both sides of the Atlantic.  A big thank you to David Lopez Mateos---I could not have done any of the research in this thesis without his guidance and watchful tutelage.  It has also been a joy collaborating with Chris Rogan, whose RestFrames concept features prominently in this thesis.  There are many other Harvard ATLAS members to whom I am indebted for their invaluable conversation, company, and companionship.  Chief among these is Tony Tong, a most stolid roommate and friend.  I would be remiss I did not also express heartfelt thanks to Karri, Emma, Ann, Paolo Giromini (a conversationalist \emph{par excellence}), William, Tomo, Tuna, Brian, Kevin, Andy, Julia, Jennifer, Stefano, Valerio, Larry, Pierluigi, Ben, Roger, and Joao.  Not to be forgotten are the many fine folks in ATLAS at large and in HSG5, in particular Paolo Francavilla and Yuji Enari.

Even shuffling between continents, Harvard has felt like home.  Sincere thanks to Lisa and Carol for being ready sources of candy, conversation, commiseration, and of course administrative support.  Thank you as well to Angela, Korin, Felice, and all the other LPPC staff who made navigating bureaucracy in three countries and two timezones so much easier.  To Erin and Sarah---we made it!

Finally, I would like to send love and thanks to my family, in particular to my mother, father, and my sister, Emily.  I could not have done it without you.
